%-------------------------
% Resume in Latex
% Author : Shicong Nie
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Shicong Nie} \\ \vspace{1pt}
    \small 13026339196 $|$ \href{mailto:x@x.com}{\underline{niebayes@gmail.com}} $|$ 
    % \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/niebayes}{\underline{github.com/niebayes}}
\end{center}

\section{Summary}
  \resumeSubHeadingListStart
    \begin{itemize}
        \item Open source enthusiast participating in Google Summer of Code with Jina AI and Open Source Promotion Plan with Apache Doris.
        \item Passionate about technology, participated in PingCAP TinyKV Bootcamp and OceanBase miniob Database Competition.
        \item Interested in distributed storage, implemented Multi-Raft, Multi-Paxos, and LSM-DB.
        \item Strong self-motivation, studied renowned open courses such as MIT 6.824, CMU 15-445, MIT 6.S081, Harvard CS265.
        \item Enthusiast in systems programming, familiar with distributed systems, database systems, and operating systems.
        \item Skilled in fundamental data structures and algorithms, familiar with programming languages such as C/C++, Go, Python, Rust.
        \item Interested in generative AI, multimodal AI, Neural Search, and AI infrastructure, actively learning related technologies.
        \item Research experience in robot localization, multi-sensor fusion, and 3D vision, have a strong foundation in mathematics.
    \end{itemize}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wuhan University of Technology}{Wuhan, China}
      {Master degree, Major in Mechanical Engineering}{Sep. 2018 -- Jul. 2021}
    \resumeSubheading
      {Wuhan University of Technology}{Wuhan, China}
      {Bachelor degree, Major in Mechanical Engineering}{Seq. 2014 -- Jul. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://github.com/niebayes/tinykv-summary}{\underline{Highly-Available Distributed Key-Value Database based on Multi-Raft}}
}{}
      {Raft, Percolator, Go}{}
      \resumeItemListStart
        \resumeItem{Consensus Layer: Implemented the Raft protocol supporting leader election, log replication, and log compaction. Implemented optimizations such as prevote, automatic step down, async apply, and flow control.}
        \resumeItem{Service Layer: Supported single-point configuration change and region split. Utilized a scheduler for automatic region scheduling to achieve load balancing. Implemented read index to improve throughput.}
        \resumeItem{Transaction Layer: Implemented MVCC based on the Percolator protocol.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/niebayes/LSM-DB}{\underline{Write-Optimized Key-Value Database based on LSM Tree}}
}{}
      {LSM tree, Rust}{}
      \resumeItemListStart
        \resumeItem{Supported insert, update, delete, and scan operations.}
        \resumeItem{Implemented the memtable backed by a B-tree and designed the file format, Bloom filter, and sparse index for the sstable.}
        \resumeItem{Designed and implemented a unified iterator interface for efficient data retrieval.}
        \resumeItem{Supported leveled, tiered, and hybrid compaction strategies.}
        \resumeItem{Implemented crash recovery using Write-Ahead Logging mechanism.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Open Source Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Summer of Code - Jina AI}{Apr. 2023 - Present}
      {Contributor}{}
      \resumeItemListStart
        \resumeItem{Enhanced the stateful executor feature based on Raft protocol, wrapped relevant Go code into Python bindings using cgo library.}
        \resumeItem{Implemented optimizations such as follower read and provided consistency mode options for service deployment in the stateful executor feature.}
        \resumeItem{Developed a highly available and high-throughput neural search service using the Jina framework and ANNLite library.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source Promotion Plan - Apache Doris}{May. 2023 - Present}
      {Contributor}{}
      \resumeItemListStart
        \resumeItem{Added SQL parsing and execution support for functions like.}
        \resumeItem{Added information about Segment Compaction in the Load Profile.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Other Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/niebayes/CMU-15-445-2020}{\underline{\textbf{bustub}}} $|$ \emph{Database Storage, C++}}{}
          \resumeItemListStart
            \resumeItem{Implemented buffer pool manager, B+ tree index, extendable hash index, lock manager, and deadlock prevention for the bustub database.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/niebayes/miniob-summary}{\underline{\textbf{miniob}}} $|$ \emph{Database SQL, C++}}{}
          \resumeItemListStart
            \resumeItem{Added parsing and execution capabilities for SQL statements such as multi-row insert, multi-col update, cross join, inner join, order by, group by, having, sub-select, and aggregation to the miniob database.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/niebayes/MIT-6.S081-summary}{\underline{ \textbf{xv6}}} $|$ \emph{Operating System Kernel, C}}{}
          \resumeItemListStart
            \resumeItem{Added features like mmap, kernel thread, copy-on-write, lazy allocation, and compensated round-robin scheduling to the xv6 operating system.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/niebayes/Balancebeam}{\underline{\textbf{balancebeam}}} $|$ \emph{Proxy Server, Rust}}{}
          \resumeItemListStart
            \resumeItem{A proxy server with features such as health checks, thread pool, connection pool, cache management, rate limiting, and load balancing.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/niebayes/DEET-Debugger}{\underline{\textbf{deet}}} $|$ \emph{Debugger, Rust}}{}
          \resumeItemListStart
            \resumeItem{A debugger with common debugging commands like breakpoints, next, continue, and backtrace.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C/C++, Go, Python, Rust} \\
     \textbf{Frameworks or Libraries}{: Jina, DocArray, Apache Doris, Apache Spark, LevelDB, Hashicorp Raft, etcd Raft} \\
     \textbf{Developer Tools}{: Linux, Git, Docker, CMake, VS Code, Vim, LaTeX} \\
     \textbf{Languages}{: Mandarin (Native), English (Fluent)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
